Deep Reinforcement Learning for Conservation Decisions

### 2021-08-16 manuscript/manuscript.Rmd
Added sentence to mention sample inefficiency

<!-- Model free is great bc we don't know the true models -->
The rapidly expanding class of model-free RL algorithms is particularly appealing given the ubiquitous presence of model uncertainty in ecological dynamics.
Rarely do we know the underlying functional forms for ecological processes.
Methods which must first assume something about the structure or functional form of a process before estimating the corresponding parameter can only ever be as good as those structural assumptions.
Frequently available ecological data is insufficient to distinguish between possible alternative models [@knape_are_2012], or the correct model may be non-identifiable with any amount of data.
Model-free RL approaches offer a powerful solution for this thorny issue.
Model-free algorithms have proven successful at learning effective policies even when the underlying model is difficult or impossible to learn [@Pong2020], as long as simulations of possible mechanisms are available.
Yet, current model-free algorithms tend to have poor sample efficiency [@sac] which may restrain them from being insightful on simulators that are slow to run.

@@

<!-- Solving 'real' problems will be hard -->
Successfully applying RL to complex ecological problems is no easy task.
Even on relatively uncomplicated environments, training an RL agent can be more challenging than expected due to an entanglement of reasons like hyperparameter instability and poor exploration that can be very difficult to resolve [@drlthatmatters; @berger-tal_exploration-exploitation_2014].
As Section 5.1 and 5.2 illustrate, it is important to begin with simple problems, including those for which an optimal strategy is already known.
Such examples provide important benchmarks to calibrate the performance, tuning and training requirements of RL.
Once RL agents have mastered the basics, the examples can be easily extended into more complex problems by changing the environment.
Yet, even in the case that an agent performs well on a realistic problem, there will be a range of open questions in using deep RL to inform decision-making. 
Since deep neural networks lack transparency [@castelvecchi_can_2016], can we be confident that the deep RL agent will generalize its past experience to new situations?
Given that there have been many examples of reward misspecification leading to undesirable behavior [@hadfield-menell_inverse_2020], what if we have selected an objective that unexpectedly causes damaging behavior?
A greater role of algorithms in conservation decision-making also raises questions about ethics and power, particularly when those algorithms are opaque or proprietary [@scoville_algorithmic_2021, @chapman_promoting_2021].

>>>>

<!-- Model free is great bc we don't know the true models -->
The rapidly expanding class of model-free RL algorithms is particularly appealing given the ubiquitous presence of model uncertainty in ecological dynamics.
Rarely do we know the underlying functional forms for ecological processes.
Methods which must first assume something about the structure or functional form of a process before estimating the corresponding parameter can only ever be as good as those structural assumptions.
Frequently available ecological data is insufficient to distinguish between possible alternative models [@knape_are_2012], or the correct model may be non-identifiable with any amount of data.
Model-free RL approaches offer a powerful solution for this thorny issue.
Model-free algorithms have proven successful at learning effective policies even when the underlying model is difficult or impossible to learn [@Pong2020], as long as simulations of possible mechanisms are available.

@@

<!-- Solving 'real' problems will be hard -->
Successfully applying RL to complex ecological problems is no easy task.
Even on relatively uncomplicated environments, training an RL agent can be more challenging than expected due to an entanglement of reasons like hyperparameter instability and poor exploration that can be very difficult to resolve [@drlthatmatters; @berger-tal_exploration-exploitation_2014].
It is also worth acknowledging that deep RL algorithms, particularly model-free algorithms, have poor sample efficiency, which could limit deep RL from being effective on environments that are slow to run [@sac].  
Thus, as Section 5.1 and 5.2 illustrate, it is important to begin with simple problems, including those for which an optimal strategy is already known.
Such examples provide important benchmarks to calibrate the performance, tuning and training requirements of RL.
Once RL agents have mastered the basics, the examples can be easily extended into more complex problems by changing the environment.
Yet, even in the case that an agent performs well on a realistic problem, there will be a range of open questions in using deep RL to inform decision-making. 
Since deep neural networks lack transparency [@castelvecchi_can_2016], can we be confident that the deep RL agent will generalize its past experience to new situations?
Given that there have been many examples of reward misspecification leading to undesirable behavior [@hadfield-menell_inverse_2020], what if we have selected an objective that unexpectedly causes damaging behavior?
A greater role of algorithms in conservation decision-making also raises questions about ethics and power, particularly when those algorithms are opaque or proprietary [@scoville_algorithmic_2021, @chapman_promoting_2021].
